Deciphering the Trends: A Comprehensive Analysis of US Birth Rates and Educational Attainment from 1980 to 2020

### 2024-02-05 outputs/paper/paper.qmd
paper.qmd update

The American Economics Association [@citewebsite] has made available a dataset that provides a thorough analysis of birth rates over a long period, broken down by a variety of demographic variables. Among the detailed records of birth rates are those by age group, education level, and marital status. The age group data covers the years 1980 to 2020 and is particularly useful for understanding how birth rates have changed over time across different age brackets. The education level data covers the years 1992 to 2019 and gives insights into how educational attainment influences birth rates. The marital status data, which covers the years 1980 to 2019, provides insight into the variations in birth rates between married and single people, reflecting changes in society and individual preferences. For this paper, there were no suitable alternative data sources

>>>>

The American Economics Association [@citewebsite] has made available a dataset that provides a thorough analysis of birth rates over a long period, broken down by a variety of demographic variables. Among the detailed records of birth rates are those by age group, education level, and marital status. Birth rates by age group and marital status are gathered from CDC Vital Statistics Births Reports. Birth rates by mother’s education is calculated by the using  National Center for Health Statistics (NCHS) Vital Statistics birth microdata, SEER population data, and the Current Population Survey. The age group data covers the years 1980 to 2020 and is particularly useful for understanding how birth rates have changed over time across different age brackets. The education level data covers the years 1992 to 2019 and gives insights into how educational attainment influences birth rates. The marital status data, which covers the years 1980 to 2019, provides insight into the variations in birth rates between married and single people, reflecting changes in society and individual preferences. For this paper, there were no suitable alternative data sources.
